NLTK: The Natural Language Toolkit

### 2002-05-15 technical/acl2002/acl02.tex
-Spelled out CFG - Added Jee Bang to acknowledgements
svn/trunk@621

The probabilistic parsing module was created as a class project for a
statistical NLP course.  The toolkit provided the basic data types and
interfaces for parsing.  The project extended these, adding a new
probabilistic parsing interface, and using subclasses to create a
probabilistic version of the CFG data structure.  These new components
were used in conjunction with several existing components, such as the
chart data structure, to define two implementations of the
probabilistic parsing interface.  Finally, a tutorial was written that
explained the basic motivations and concepts behind probabilistic
parsing, and described the new interfaces, data structures, and
parsers.

@@

We are indebted to our students for feedback on the toolkit,
and to anonymous reviewers and the workshop organizers for comments
on an earlier version of this paper.  We are grateful to Mitch
Marcus and the Department of Computer and Information Science
at the University of Pennsylvania for sponsoring the work
reported here.

>>>>

The probabilistic parsing module was created as a class project for a
statistical NLP course.  The toolkit provided the basic data types and
interfaces for parsing.  The project extended these, adding a new
probabilistic parsing interface, and using subclasses to create a
probabilistic version of the context free grammar data structure.
These new components were used in conjunction with several existing
components, such as the chart data structure, to define two
implementations of the probabilistic parsing interface.  Finally, a
tutorial was written that explained the basic motivations and concepts
behind probabilistic parsing, and described the new interfaces, data
structures, and parsers.

@@

We are indebted to our students for feedback on the toolkit, and to
anonymous reviewers, Jee Bang, and the workshop organizers for
comments on an earlier version of this paper.  We are grateful to
Mitch Marcus and the Department of Computer and Information Science at
the University of Pennsylvania for sponsoring the work reported here.
